Inefficient Concessions and Mediation

### 2020-11-29 notes.tex
create sections in notes.tex; start mediator section with IC constraints

\vskip.3in
\un{June 6, 2017}\\
Want to develop result showing that mediator increases potential for peace
\begin{itemize}
	\item i.e. want to show mediator makes (Trust, Trust) an equilibrium over a larger parameter space than without mediator
\end{itemize}

@@

\newpage
To-do list after Venice CesIfo 06/15/17:
\begin{itemize}
	\item Jim Fearon: maybe get rid of repeated game and just parameterize a one-shot game (doens't work because concessions required for separation are too large; require future to recoup cost)
		\begin{itemize}
			\item he has a paper about concessions being used against you; he also gave me the reference for another one but I've forgotten it
		\end{itemize}

@@

\newpage
Review 1 from EJPE (Email from Toke Aidt, August 19, 2018): \\

>>>>

\vskip.3in

\section{Make mediator work}
\un{November 29, 2020}\\
In making revisions in April 2020 to respond to the EJPE referee reports, I discovered the IC constraint does not hold for the low type in Section 5: Mediation. Here I will see what adjustments might make the mediator work.\\

IC constraints for Mediation
\begin{itemize}
	\item low type IC:
		$$X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h $$
			\begin{itemize}
				\item If a low type reveals truthfully: you get $X_{FF}$ and no gift with probability $p$; you get the same with probability $(1-p)$ (you need both countries to be high types in order to do anything)
				\item If a low type lies: get $X_{FT}$ and give gift ($g_h$) and receive gift ($eg_h$) with probability $p$; $X_{FF}$ again with probability $(1-p)$
					\begin{itemize}
						\item High type gives gift with efficiency $e=1$, so gift giving and receiving cancels out
					\end{itemize}
				\item Relative to Section 4.2, there is no $peg_h$ on the RHS: no benefit of getting the gift from the high type
					\begin{itemize}
						\item NEXT STEP: CHECK THESE CLAIMS ABOUT THE RELATIONSHIP TO SECTION 4.2
					\end{itemize}
			\end{itemize}
	\item high type IC:
		$$pX_{TT}^h+(1-p)X_{FF}^h - pg_h +peg_h \geq X_{FF}^h $$
\end{itemize}

\vskip.5in
\section{Develop result: mediator increases potential for peace}
\un{June 6, 2017}

\begin{itemize}
	\item i.e. want to show mediator makes (Trust, Trust) an equilibrium over a larger parameter space than without mediator
\end{itemize}

@@

\newpage
\section{To-do list after Venice CesIfo 06/15/17}
\begin{itemize}
	\item Jim Fearon: maybe get rid of repeated game and just parameterize a one-shot game (doens't work because concessions required for separation are too large; require future to recoup cost)
		\begin{itemize}
			\item he has a paper about concessions being used against you; he also gave me the reference for another one but I've forgotten it
		\end{itemize}

@@

\newpage
\section{Review 1 from EJPE (Email from Toke Aidt, August 19, 2018)}
